### 2016-04-26 papers/thesis-vischer/Thesis.tex
More plot discussion, more information on Carnahan Starling Tests skipped!

\subsubsection{Carnahan-Starling Equation of State}
In order to determine the filling fraction step size during thermodynamic integration we must find changes in filling fraction that yield a suitably-sized change in the system's absolute free energy. To do this we use the Carnahan-Starling equation of state, shown in Eq.~\ref{C-S-eq}.
\begin{align}
    F(\eta) &= \frac{4\eta - 3\eta^2}{(1-\eta)^2}   
    \label{C-S-eq}  
\end{align} 
where $\eta$ is the filling fraction. The Carnahan-Starling equation of state is an excellent approximation for low-density hard spheres. Close to solidification, near $\eta_{freeze} \approx .5$, this equation of state fails. Thankfully, we are only concerned with filling fractions slightly or significantly below this value, and so the Carnahan-Starling equation of state is an invaluable tool.\\ \ignore{BLAH}
Combining Eq.~\ref{C-S-eq} with a simple bisection method allows for control of the filling fraction step size given a desired change in free energy. We determined that steps yielding an approximate change in specific absolute free energy of $\Delta F^{abs}/NT = \ln(2)$ through trial and error - smaller step sizes unnecessarily increased simulation time and larger step sizes tended to shrink too quickly causing the simulation to miss relevant states in the system.

@@

Figures ~\ref{F-T} and ~\ref{F-eta} show preliminary free energy calculations.
\begin{figure}[H]
\centering
    \includegraphics[width=.75\textwidth]{Fexc-vs-T.pdf}
    \caption{Preliminary results for excess specific free energy as a function of temperature with each quantity scaled by well depth $\epsilon$. The vertical line at $T/\epsilon = 0.3$ is the lowest temperature at which our statistics are trustworthy.}
    \label{F-T}
\end{figure}

>>>>

\subsubsection{Carnahan-Starling Equation of State}
In order to determine the filling fraction step size during thermodynamic integration we must find changes in filling fraction that yield a suitably-sized change in the system's absolute free energy. To do this we use the Carnahan-Starling equation of state, shown in Eq.~\ref{C-S-eq}.
\begin{align}
    F(\eta) &= \frac{4\eta - 3\eta^2}{(1-\eta)^2}   
    \label{C-S-eq}  
\end{align} 
where $\eta$ is the filling fraction. The Carnahan-Starling equation of state was developed to model hard spheres at low densities in the thermodynamic limit. We are very much concerned with cells significantly far from the thermodynamic limit. Thankfully, we are only concerned with filling fractions slightly or significantly below this value, and so the Carnahan-Starling equation of state is an invaluable tool.\\
Combining Eq.~\ref{C-S-eq} with a simple bisection method allows for control of the filling fraction step size given a desired change in free energy. We determined that steps yielding an approximate change in specific absolute free energy of $\Delta F^{abs}/NT = \ln(2)$ through trial and error - smaller step sizes unnecessarily increased simulation time and larger step sizes tended to shrink too quickly causing the simulation to miss relevant states in the system. This step size corresponds to changing the entropy by $1/2$ each step.

@@

Figures ~\ref{F-T} through ~\ref{F-eta} show several computed thermodynamic quantities for the scrunched system. Each  It is worth noting that the two succeeding plots with respect to density have been interpolated; with a fixed cell size, it is only possible to simulate discrete filling fractions. The intervening points have been filled in using the Carnahan-Starling equation of state.  
\begin{figure}[H]
\centering
    \includegraphics[width=.75\textwidth]{Fexc-vs-T.pdf}
    \caption{Excess specific free energy as a function of temperature with each quantity scaled by well depth $\epsilon$. }
    \label{F-T}
\end{figure}
